\forestclaw: Hybrid forest-of-octrees AMR for hyperbolic conservation laws

### 2013-07-30 docs/parco13/paper.tex
Address two concerns

\usepackage{amsmath,amssymb}
\usepackage{cite}
\usepackage{color}
\usepackage{graphicx}
\usepackage{url}
\usepackage{xspace}

@@

To facilitate hardware acceleration for parallel dynamic AMR, we
build upon the forest-of-octrees paradigm because of its low overhead
and proven scalability \cite{BursteddeWilcoxGhattas11}.  This approach
identifies each octree leaf with a mesh element.  \alert{The presented work goes beyond the traditional high-order element and defines each element to
be a dense computational patch with $m^d$ DOFs.}  In fact, this approach
resembles block-structured AMR \cite{be-ol:1984, be-co:1989,
% be-le:1991 (cited below)
ColellaGravesKeenEtAl07,
BerzinsLuitjensMengEtAl10} except that the
patches are not overlapping,
% (except in ghost cell regions),
% CB: we comment on this later in Section 4.
which enables us to capitalize on our
previous experience with scalable FE solvers for PDEs
\cite{BursteddeStadlerAlisicEtAl13}.  The \clawpack software
\cite{LeVeque97} provides a popular implementation of such a patch.
It has been designed to solve hyperbolic conservation laws
% on a uniform compute patch
and successfully used in the context of block-structured AMR
\cite{be-le:1991, amrclaw, Berger:2011du}.
\comment{Review 1 points out that the statement in red may not be what we are intending to say here.  Mainly the distinction between claiming better convergence then a high-order method (which I think is not what we are saying) and just stating that our elements are patches themselves as opposed to a single DOF.}

@@

\begin{figure}
\begin{center}
\includegraphics[width=.4\columnwidth]{../figs_misc/forest_stacked}
\hspace{.05\columnwidth}
\includegraphics[width=.4\columnwidth]{../figs_misc/cubed3}
\end{center}
\caption{Left: Forest of two quadtrees, partitioned among three MPI processes.
Each quadtree has its own coordinate orientation.  The situation in 3D
(octrees) is analogous.  Right: The leaves in a forest of six quadtrees that
serves as the computational domain for the cubed sphere.  An adhoc refinement
pattern has been 2:1 balanced in terms of neighbor sizes and partitioned
between five MPI processes (the three middle ones are shown from black to
white).}
\label{fig:cubed3}
\end{figure}

>>>>

\usepackage{amsmath,amssymb}
\usepackage{cite}
\usepackage{color}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{url}
\usepackage{xspace}

@@

To facilitate hardware acceleration for parallel dynamic AMR, we
build upon the forest-of-octrees paradigm because of its low overhead
and proven scalability \cite{BursteddeWilcoxGhattas11}.  This approach
identifies each octree leaf with a mesh element.  The presented work does not
construct a traditional high-order element but defines each element to be a
dense computational patch with $m^d$ DOFs.  In fact, this approach
resembles block-structured AMR \cite{be-ol:1984, be-co:1989,
% be-le:1991 (cited below)
ColellaGravesKeenEtAl07,
BerzinsLuitjensMengEtAl10} except that the
patches are not overlapping,
% (except in ghost cell regions),
% CB: we comment on this later in Section 4.
which enables us to capitalize on our
previous experience with scalable FE solvers for PDEs
\cite{BursteddeStadlerAlisicEtAl13}.  The \clawpack software
\cite{LeVeque97} provides a popular implementation of such a patch.
It has been designed to solve hyperbolic conservation laws
% on a uniform compute patch
and successfully used in the context of block-structured AMR
\cite{be-le:1991, amrclaw, Berger:2011du}.
% \comment{Review 1 points out that the statement in red may not be what we are
% intending to say here.  Mainly the distinction between claiming better
% convergence then a high-order method (which I think is not what we are saying)
% and just stating that our elements are patches themselves as opposed to a
% single DOF.}
% CB: reworded the criticized statement above.

@@

\begin{figure}
\begin{center}
\includegraphics[width=.4\columnwidth]{../figs_misc/forest_stacked}
\hspace{.05\columnwidth}
\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},
                    x=1mm, y=1mm]
  \node at (0,0) {
    \includegraphics[width=.4\columnwidth]{../figs_misc/cubed3}
  };
  \node [fill=white, inner sep=2pt] at (28, 10) {1};
  \node [fill=white, inner sep=2pt] at (5, 27) {2};
  \node [fill=white, inner sep=2pt] at (41, 27) {2};
  \node [fill=white, inner sep=2pt] at (28, 36) {3};
\end{tikzpicture}
%\includegraphics[width=.4\columnwidth]{../figs_misc/cubed3}
\end{center}
\caption{Left: Forest of two quadtrees, partitioned among three MPI processes.
Each quadtree has its own coordinate orientation.  The situation in 3D
(octrees) is analogous.  Right: The leaves in a forest of six quadtrees that
serves as the computational domain for the cubed sphere.  An adhoc refinement
pattern has been 2:1 balanced in terms of neighbor sizes and partitioned
between five MPI processes (the three middle ones out of $0 \ldots 4$
are shown from black to white).}
\label{fig:cubed3}
\end{figure}
